Behavior Driven Development in Haskell

### 2012-05-23 paper.tex
Add section on combining specs

>>>>

\subsection{Combining multiple specs}

\begin{quote}
\emph{This is optional, so we can skip it, if necessary.}
\end{quote}

\begin{itemize}
\item We create a spec file for each source file
\item By convention, spec files end in Spec.hs
\end{itemize}

\noindent If we have a source tree like so:

\begin{quote}
\begin{verbatim}
src/Foo.hs
src/Foo/Bar.hs
src/Baz.hs
\end{verbatim}
\end{quote}

\noindent We would end up with the following spec files.

\begin{quote}
\begin{verbatim}
test/FooSpec.hs
test/Foo/BarSpec.hs
test/BazSpec.hs
\end{verbatim}
\end{quote}

\begin{itemize}
\item We still want to combine those specs into a single spec.
\item By convention we put the combined spec into test/Spec.hs
\end{itemize}

\begin{quote}
\begin{verbatim}
import Test.Hspec.Monadic

import qualified FooSpec
import qualified Foo.BarSpec
import qualified BazSpec

main :: IO ()
main = hspecX $ do
  describe "Foo"     FooSpec.spec
  describe "Foo.Bar" Foo.BarSpec.spec
  describe "Baz"     BazSpec.spec
\end{verbatim}
\end{quote}

\begin{itemize}
\item We use a preprocessor (http://hackage.haskell.org/package/hspec-discover) to automatically generate this boilerplate.
\end{itemize}

\begin{quote}
\begin{verbatim}
{-# OPTIONS_GHC -F -pgmF hspec-discover #-}
\end{verbatim}
\end{quote}
